\documentclass[tikz]{article}
\title{\textbf{Sheet 4}\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=6cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{God A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{People are capable to figure things out on their own.}
		\item{Things are bad just because of some intuition about god.}
		\item{We are rich in many other ways.}
		\item{God were real.}
		\item{I believe in a different god.}
		\item{Believe in God with confidence.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{You don't believe in God.}
		\item{A god exists or not.}
		\item{He is the one true God.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{(X) God doesn't exist. (Y) Wager then, without hesitation, that He exists.}
		\item{(X) Science doesn't provide us with truth. (Y) More about how the world works.}
		\item{(X) Science doesn't provide us with truth. (Y) The explanation doesn't have to be true to be useful, just consistent with most of the evidence.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Religious people don't base their morality on evidence.}
		\item{We'll be arguing about religions and not God.}
		\item{Bad things happen to innocent people.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{God}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Not believe in god.}
		\item{People don't need a god.}
		\item{He is the christian god.}
        \end{itemize}
      \item{Religion}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{You first brought up religion.}
		\item{Difference with theists is they follow their religion.}
		\item{Back into many ancient religions a flood was caused by the Gods.}
        \end{itemize}
      \item{Science}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{By using reason and science.}
		\item{A god doesn't disprove science and vice-versa.}
		\item{Some things can't be explained by science.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Many can testify of the existence of God.}
		\item{God created the world in six days.}
		\item{People don't need God or religion to do good things for others.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{What is the point?}
		\item{He does exist?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{God B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{That the people that seem to blame god for everything are the ones that don't believe in him?}
		\item{There is a god and he lives in all of us.}
		\item{You do know your tagged as yes don't you?}
		\item{No, i don't. i can ramble on about why but i'm not going to.}
		\item{So it was made up?}
		\item{I agree if god truly existed then we would have more resources and we would have more help}
		\item{Therefore,there cannot be absolute.}
		\item{God might exist but no one knows.}
		\item{People only believe in god because they need to justify life. and other things.}
		\item{God has been around a lot longer than this debate}
		\item{What pyrus said. the bible is proof of his existence.}
		\item{God does exist, whether hes actually real or just a thought hes real. god ownz}
		\item{I really don't know what you were aiming at here.}
		\item{What about the creation story with the world being created in 7 days. i do not think science can ever support that story.}
		\item{If it is a question ask your self . if it is an argument only time will explain you clearly.}
		\item{You mean like the flying spaghetti monster?no. not without some kind of evidence.}
		\item{Why? i don't get how it's confusing?}
		\item{Who says the creator of all those laws is bound by them?}
		\item{I believe in god so i won't go to hell.}
		\item{All we realize only exists in our mind.}
		\item{Very well said; my hats off to you.}
		\item{God doesn't hate you.}
		\item{God does exist man}
		\item{Your grammar is a little off}
		\item{So it was made up?}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
