\documentclass[tikz]{article}
\title{\textbf{Sheet 6}\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=4cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{indyref (days before) A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{I am voting yes for scotland wish.}
		\item{A yes vote all over cathedral in edinburgh.}
		\item{I would not be sleeping thursday night.}
		\item{Scotland get independence.}
		\item{I am half scottish.}
		\item{Tomorrow is the day.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Vote yes on thursday.}
		\item{I was in scotland right now.}
		\item{I am proud to be scots.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{(X) I am a vote but the efforts up here have been shit. (Y) Despite being scottish I can't vote.}
		\item{(X) She wants to tackle poverty and protect our nhs. (Y) Firstly protect the nhs.}
		\item{(X) Getting involved on behalf of the campaign. (Y) Involved on behalf of the campaign.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Scottish nhs would face black hole under independence.}
		\item{Team westminster doesn't work for the people.}
		\item{Prices go up on friday after vote.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Scotland}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{As an englishman I want scotland to stay.}
		\item{Come on scotland, 4 nations.}
		\item{Go ahead in scotland.}
        \end{itemize}
      \item{Vote}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Please scotland vote.}
		\item{I don't get a vote.}
		\item{I can't vote on thursday.}
        \end{itemize}
      \item{Salmond}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{We are all nick robinson salmond \& co just don answer.}
		\item{Many people are trusting salmond and word.}
		\item{Now backing off salmond, including the sun.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Snp wants independence but wants a currency union.}
		\item{David beckham also backs the no vote for scottish independence.}
		\item{You came back for the campaign and the party, historic times scottish star.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Have they even told us?}
		\item{People know?}
		\item{If scotland goes?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{indyref (days before) B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Cheerio to the bbc}
		\item{I there is a no vote . .}
		\item{Scotland . in charge of}
		\item{And what if we are ? ? and what ?}
		\item{Yes , yes , yes , yes , yes , yes , yes}
		\item{You can be for but not salmond \& socialism .}
		\item{Please get on with it then .}
		\item{Nope that will be votes that do that}
		\item{Have voters seen this ?}
		\item{Why i back the ' yes ' campaign - from england}
		\item{People at my door my ak at}
		\item{Well because i am scottish .}
		\item{Who them or us ?}
		\item{Forget all about tomorrow}
		\item{So so so so true . means they didn't care before}
		\item{More like leave now .}
		\item{Just your opinion , man .}
		\item{Not as good as this one}
		\item{An emotional appeal by}
		\item{When did he say that ?}
		\item{Never take . our freedom}
		\item{Everyone has their own opinion}
		\item{Scottish independence uk rip ?}
		\item{Better ? lulz ! go scots}
		\item{Who would believe any westminster}
		\item{Really cannot see through his}
		\item{How does this poll add up ?}
		\item{Oi ! me too , lol .}
		\item{Its still dark out . yeah}
		\item{Wow ! fishing was great today}
		\item{Only think about money ?}
		\item{Time she used some}
		\item{Anything we should know ? ?}
		\item{Hope over fear ? or false hope over facts ?}
		\item{Gordon brown being absolutely brilliant tonight}
		\item{Very last night ha}
		\item{Stay together , stay in real world}
		\item{Nhs lies come from}
		\item{Interesting 5 years old voting ?}
		\item{Final day of referendum}
		\item{Not want said today}
		\item{Been a long road .}
		\item{Let us put future in hands . let us put future}
		\item{Another big agree mr . t}
		\item{Oh dear x 2}
		\item{Free my country , free my land}
		\item{Were we right guys ? ? ?}
		\item{Love my new pen}
		\item{Kicking us off here}
		\item{Which way are you}
		\item{Is a wee ned}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
