\documentclass[tikz]{article}
\title{\textbf{Sheet 3} Debate Comparison Evaluation\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=6cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{Guns A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{People are automatically responsible.}
		\item{Guns were illegal.}
		\item{They are no more dangerous than any other firearm out there.}
		\item{Criminals have guns.}
		\item{Clearly having guns.}
		\item{Carry a loaded gun.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Keep arms in our homes.}
		\item{Kill many people.}
		\item{Own a gun there.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{(X) I should not have a gun. (Y) Guns make you safer.}
		\item{(X) Concealed carry permit holder. (Y) Carry permit for 20 years.}
		\item{(X) Bear arms, in actuality. (Y) Bear arms for the purpose of self-defense.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{I grew up in a house hold around firearms.}
		\item{You need a machine gun to kill a deer.}
		\item{You take guns off the streets.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Gun}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{On how to use guns.}
		\item{Get guns off the street.}
		\item{Them carry a gun.}
        \end{itemize}
      \item{People}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{People kill people.}
		\item{Guns don't kill people.}
		\item{The militia are the people.}
        \end{itemize}
      \item{Government}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Protect ourselves from a tyrannical government.}
		\item{Fighting a tyrannical government.}
		\item{Limit democratically-elected governments.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{More people are accidentally killed by their own guns.}
		\item{Get the guns and kill the other people.}
		\item{Cars kill many more people per year than guns.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Do you really need a machine gun to kill a little deer?}
		\item{Do guns make you safer?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{Guns B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Just to the british citizens, aye? no. to the majority of the world.}
		\item{No if you have a guns license}
		\item{I disagree with maugatar, for the simple fact that it is people with guns that kill people.}
		\item{No, noyb, and no.}
		\item{It says the right of the people as in citizens, not militia.}
		\item{All we need is good gun control. and by "good gun control" i mean two hands on the gun}
		\item{Where are your statistics? if there were such incidents, the media would be all over it.}
		\item{As long as people who have guns use they responsibly they should never be banned}
		\item{The right to "bear arms" in the 2nd amendment includes an individual right}
		\item{Making more laws just makes shooting someone more illegal not less common}
		\item{That has always been my thoughts states side.}
		\item{Psst, criminals don't plan on following gun laws, so banning guns will not prevent robberies or crimes.}
		\item{Thats what i said}
		\item{An assault weapons ban encourages organized crime}
		\item{Guns are very easy to get and anyone can use them to kill people.}
		\item{Sorry to say it, but it is probably true.}
		\item{Outlaw guns, then only outlaws will have guns.}
		\item{We need to protect ourselves}
		\item{You said it all.}
		\item{Clinton gun ban.com}
		\item{No if you have a guns license}
		\item{Thats what i said}
		\item{You said it all.}
		\item{No, noyb, and no.}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
