\documentclass[tikz]{article}
\title{\textbf{Sheet 5}\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=6cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{\#Indyref Tweets (on Referendum day) A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{People are still voting no.}
		\item{Me wake up to a yes vote.}
		\item{They will be worse tomorrow.}
		\item{Voting for independence.}
		\item{Fingers crossed for wee secret sneaky yes vote.}
		\item{Go scotland today.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{I am half scottish and I believe.}
		\item{Today is the day.}
		\item{Us stay together.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{(X) I don't want to live in a 3rd world country. (Y) Live in a 3rd world country.}
		\item{(X) I am away to vote now and seeing. (Y) You have not voted yet.}
		\item{(X) You are the hope and dream of william wallace. (Y) I really do hope.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Scotland - stay in the union.}
		\item{You get to the polling station today.}
		\item{Us hope for a no vote.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Scotland}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Come on scotland fast.}
		\item{I am sure scotland.}
		\item{I want scotland to be a democratic country.}
        \end{itemize}
      \item{Vote}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Today I am voting.}
		\item{Away to get my vote in.}
		\item{Just cast my vote.}
        \end{itemize}
      \item{Today}
        \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Today I am voting.}
		\item{Proudly wearing today.}
		\item{Make a terrible mistake today.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Really hope scotland vote no today.}
		\item{The good people of scotland voted no.}
		\item{I really hope scotland vote yes today.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{If you vote no, how long?}
		\item{You voting?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{\#Indyref Tweets (on Referendum day) B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
		\item{Follow the vote in}
		\item{Just has to be a}
		\item{Scotland is not spain}
		\item{Thinking of you today}
		\item{And so it begins}
		\item{I have more respect for}
		\item{Scottish referendum yes : no}
		\item{We are better than this}
		\item{People do trade with my country}
		\item{Conservative on , if you will}
		\item{Stick that up your}
		\item{The day ! all i am saying}
		\item{Why has most words from been negative , ' ' you cannot ' ' ' ' you would not ' ' ' ' we ' ' we can ' ' ' ' we will ' ' ' believe}
		\item{Us , now , or never}
		\item{Hope they get gubbed .}
		\item{Keep britain as one .}
		\item{Scotland : what was life like ?}
		\item{Look at our future king}
		\item{Let me say something : better together .}
		\item{But it should be}
		\item{Actually worried about tomorrow}
		\item{Good luck to you scots voting}
		\item{Please don go independent}
		\item{Scottish independence track - - by}
		\item{Voted - burst out crying this i out time}
		\item{Hope uk stays uk}
		\item{Too right ! here goes}
		\item{Such an amazing feeling}
		\item{Not many there , are there ?}
		\item{Wait and see wait and see}
		\item{Give them freedom , give them them}
		\item{Another great british article}
		\item{How are your votes going ?}
		\item{Happy everyone ! make me proud}
		\item{When you need him .}
		\item{Because we want that}
		\item{He said we were}
		\item{Wee pre polling station}
		\item{Hoping head wins over heart}
		\item{Come on you voters}
		\item{Vote done a big}
		\item{Look who is in}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
