\documentclass[tikz]{article}
\title{\textbf{Sheet 2}\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=6cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{Abortion A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Abortion should be illegal.}
      \item{Life begins at conception.}
      \item{Abortion is wrong.}
      \item{A fetus is a person.}
      \item{Animals and fetuses have rights.}
      \item{Abortion is still murder.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{She is pregnant and the baby.}
          \item{I'm pro-choice for all those babies.}
          \item{The fetus is not a human being.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{(X) Seriously : I am against all abortion. (Y) Not to have an abortion.}
          \item{(X) You have no right to any life. (Y) Taking the life of another person.}
          \item{(X) You judge someone as a murderer and hell-bound. (Y) She can't have an abortion.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{A human being refers to a specific living organism of a specific kind.}
          \item{The human life cycle begins at conception.}
          \item{I must not care about the mother.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Abortion}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{Seek third-term partial birth abortions.}
          \item{Banning partial birth abortion.}
          \item{Get an abortion in no way.}
        \end{itemize}
      \item{Woman}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{You are a very brave and strong woman.}
          \item{After a woman has an abortion.}
          \item{Saving to the pregnant woman.}
        \end{itemize}
      \item{Fetus}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{Killing an innocent fetus.}
          \item{They are fetuses, not human beings.}
          \item{All of us were once a fetus.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{Find the balance between a womans choice and protecting human life.}
          \item{Get abortions and campaign for pro-choice laws.}
          \item{The constitution doesn't provide rights or personhood to a fetus.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{Do you value your life above that of 3,613 strangers?}
          \item{When does HUMAN life begin?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{Abortion B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{So you think it is a baby, the moment the sperm fertilizes the egg?}
      \item{Might want to change "man" to "human".}
      \item{Judaism holds that life begins at birth and abortion is not murder}
      \item{The majority of americans oppose abortions}
      \item{I chose to be pro life didn't i?}
      \item{What evidence do you have for this?}
      \item{God exists in the unborn as in the born}
      \item{Faithful catholic are there still any?}
      \item{I don't know a woman who would choose rape over an infection.}
      \item{I'm confused with your argument.are you saying that it should be legal or illegal?}
      \item{Not if you get raped, no.}
      \item{Your right they shouldnt be haveing sex but they do and they are not about to stop if they dont even want to wear a condom}
      \item{What about the child who has no say? when do we start holding people accountable for their actions?}
      \item{Thats not so any more}
      \item{Yes, all innocent life. but that depends on how you define innocent life.}
      \item{Thats what the other debater said. unless it was an accident or her life was in dangerr}
      \item{Since createdebate won't let me close my account, i will delete my posts.}
      \item{You just compared the life of a human fetus to a snail. .}
      \item{No not for now it's need.}
      \item{What is a separate, living being?}
      \item{Then why are you pro choice!?}
      \item{Dead bodies do not have rights.}
      \item{I like the symmetry in this definition.}
      \item{Roe v wade.org}
      \item{Catholics united for life}
      \item{National right to life}
      \item{Roe v wade.org}
      \item{Roe v wade.org}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
