\documentclass[tikz]{article}
\title{\textbf{Sheet 1}\vspace{-9ex}}
\date{}

\usepackage{fullpage, url, enumitem, multicol, titling, titlesec, tikz}
\usepackage[a4paper,margin=1cm]{geometry}
\setlength{\droptitle}{-5em}

\pagenumbering{gobble}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

\newcommand\TBox[3][]{%
  \tikz\node[draw,thick,minimum height=6cm,text width=#2,align=left,#1] {#3};}

\begin{document}
  \maketitle

  \begin{multicols}{2}
    \subsection*{Gay Rights A}
    People disagree on these points:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Homosexuality is wrong.}
      \item{Same-sex marriages should be legal.}
      \item{They'd be good parents.}
      \item{Allow same-sex marriage.}
      \item{Have gay children.}
      \item{Gay is a choice.}
    \end{itemize}

    Commonly occurring points made in the discussion were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Homosexuality is a sin.}
      \item{Just because you are a homosexual.}
      \item{Raise children so much.}
    \end{itemize}

    Users that talk about X often talk about Y.
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{(X) They don't have equal rights. (Y) Some people are gay.}
      \item{(X) Gay marriage hurts everyone. (Y) Of democracy you can't marry a woman.}
      \item{(X) A man lie with a beast. (Y) They shall surely be put to death.}
    \end{itemize}

    Common points made in the discussion linking terms were:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{You allow homosexual couples to marry.}
      \item{In conclusion, the phrase gay marriage hurts users of language.}
      \item{A gay person won't get into heaven.}
    \end{itemize}

    Points for commonly discussed topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{God}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{As they've just created their own god.}
          \item{GOD is also a just and righteous GOD.}
          \item{Please their foreign god.}
        \end{itemize}
      \item{Marriage}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{I am against marriage personally.}
          \item{The only argument people opposed to gay marriage.}
          \item{Use the word marriage.}
        \end{itemize}
      \item{Man}
        \begin{itemize}[noitemsep,nolistsep,label={}]
          \item{Marriage is between a man and a woman.}
          \item{I am a straight man with gay friends.}
          \item{Marriage should be defined as between a man and a woman.}
        \end{itemize}
    \end{itemize}

    Points about multiple topics:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{The Bible opposes homosexuality and gay marriage.}
      \item{Regardless of marriage, homosexuality will always exist.}
      \item{Children of gay parents might be more open to homosexual activity.}
    \end{itemize}

    People ask questions like:
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{How do we decide?}
      \item{Do I have rights?}
    \end{itemize}

    % --------------------------------------------------------------------------
    \vfill
    \columnbreak
    % --------------------------------------------------------------------------

    \subsection*{Gay Rights B}
    \begin{itemize}[noitemsep,nolistsep,label={}]
      \item{Congress is the primary legislative organ of the state.}
      \item{They chose to be gay?}
      \item{Are you a christ follower?}
      \item{I know socialist; she only has one account and so do i.}
      \item{It's a website that lists churches that welcome lgbt people.}
      \item{It would upset me}
      \item{Should be but not}
      \item{And how many shellfish have you eaten in your life?}
      \item{The case for gay marriage". the economist. february 26th, 2004}
      \item{That is as far from the truth as one can get! there are no statistics that show that your take on this is true.}
      \item{I agree with just about everything you just said. thank you}
      \item{Are you going to leave me alone or what?}
      \item{Parents are people who are legally married who actually love each other and their children and who stay together. not just gay sex partners.}
      \item{Every child should be raised by heterosexual parents. gay couples shouldn't adopt, they are not parents.}
      \item{Even if god exists, why would he give a shit if two men kissed each other?}
      \item{I think we all need to revisit the context of what paul said.}
      \item{These are very, very different things.}
      \item{What about those christian churches that marry homosexuals?}
      \item{I'm yet to see any comedy from joe.}
      \item{Of course it does}
      \item{Cause there sick in the head.}
      \item{Is incest a sin?}
      \item{That's funny. one up vote for you}
      \item{Very well written. thanks}
      \item{I liked your response.}
      \item{Should be but not}
      \item{Of course it does}
    \end{itemize}
  \end{multicols}

  Comments:

  \medskip

  \TBox[fill=black!3]{0.92\textwidth}{}

\end{document}
